---
title: "logisticregression Package Walkthrough"
author: "Erica Maul, Michael Zirpoli, Rukesh Gusain"
date: "2022-12-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The function of this vignette is to demonstrate how to use the functions in our package titled "logisticregression". The following examples use data from a csv file available on the STAT 6210 Canvas page.


First, install the package and assign the data.
```{r include=FALSE}
library(devtools)
install_github("AU-R-Data-Science/Final-Project-Group-11/logisticregression/")
library(logisticregression)
cropdata<-read.csv("crop.data.csv")
y <- cropdata$density
X <- as.matrix(cropdata[,-1])
```


Example of the function "initial_beta"
```{r}
initial_beta(X=X, y=y)
```

Example of the function "loss_func"
```{r}
loss_func(y=y, X=X, beta=initial_beta(X,y))
```

Example of the function "beta_hat"
```{r}
beta_hat()
```

Example of the function "data"
```{r}
data(X=X, y=y)
```

Example of the function "bootstrap"
```{r}
bootstrap(data=data(y=y,X=X), alpha=.05, B=20)
```

Example of the function "logistic_curve"
```{r}
logistic_curve(data=data(y=y,X=X), predictor="yield", beta_hat = beta_hat())
```

Example of the function "metrics"
```{r}
metrics(X=X, beta=initial_beta(X=X, y=y), beta_hat=beta_hat(), cutoff=.6)
```

Example of the function "metricsplot"
```{r}
metricsplot(metric="Accuracy")
```
